---
title: "Mini Data Analysis Milestone 2"
output: github_document
---

*To complete this milestone, you can either edit [this `.rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-2.Rmd) directly. Fill in the sections that are commented out with `<!--- start your work here--->`. When you are done, make sure to knit to an `.md` file by changing the output in the YAML header to `github_document`, before submitting a tagged release on canvas.*

# Welcome to the rest of your mini data analysis project!

In Milestone 1, you explored your data. and came up with research questions. This time, we will finish up our mini data analysis and obtain results for your data by: 

- Making summary tables and graphs 
- Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

We will also explore more in depth the concept of *tidy data.* 

**NOTE**: The main purpose of the mini data analysis is to integrate what you learn in class in an analysis. Although each milestone provides a framework for you to conduct your analysis, it's possible that you might find the instructions too rigid for your data set. If this is the case, you may deviate from the instructions -- just make sure you're demonstrating a wide range of tools and techniques taught in this class.

# Instructions

**To complete this milestone**, edit [this very `.Rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-2.Rmd) directly. Fill in the sections that are tagged with `<!--- start your work here--->`.

**To submit this milestone**, make sure to knit this `.Rmd` file to an `.md` file by changing the YAML output settings from `output: html_document` to `output: github_document`. Commit and push all of your work to your mini-analysis GitHub repository, and tag a release on GitHub. Then, submit a link to your tagged release on canvas.

**Points**: This milestone is worth 50 points: 45 for your analysis, and 5 for overall reproducibility, cleanliness, and coherence of the Github submission. 

**Research Questions**: In Milestone 1, you chose two research questions to focus on. Wherever realistic, your work in this milestone should relate to these research questions whenever we ask for justification behind your work. In the case that some tasks in this milestone don't align well with one of your research questions, feel free to discuss your results in the context of a different research question.

# Learning Objectives

By the end of this milestone, you should:

-   Understand what *tidy* data is, and how to create it using `tidyr`.
-   Generate a reproducible and clear report using R Markdown.
-   Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

# Setup

Begin by loading your data and the tidyverse package below:

```{r, message = FALSE}
library(datateachr) # <- might contain the data you picked!
library(tidyverse)
```

# Task 1: Process and summarize your data 

From milestone 1, you should have an idea of the basic structure of your dataset (e.g. number of rows and columns, class types, etc.). Here, we will start investigating your data more in-depth using various data manipulation functions. 

### 1.1 (1 point) 

First, write out the 4 research questions you defined in milestone 1 were. This will guide your work through milestone 2:

<!-------------------------- Start your work below ---------------------------->
1. Do newer apartments have more elevators?
2. Does the year of the apartment built affect the presence of fire alarms?
3. Are newer apartments taller?
4. Do newer apartments come with more parking spaces?
<!----------------------------------------------------------------------------->

Here, we will investigate your data using various data manipulation and graphing functions.

### 1.2 (8 points)

Now, for each of your four research questions, choose one task from options 1-4 (summarizing), and one other task from 4-8 (graphing). You should have 2 tasks done for each research question (8 total). Make sure it makes sense to do them! (e.g. don't use a numerical variables for a task that needs a categorical variable.). Comment on why each task helps (or doesn't!) answer the corresponding research question.

Ensure that the output of each operation is printed!

Also make sure that you're using dplyr and ggplot2 rather than base R. Outside of this project, you may find that you prefer using base R functions for certain tasks, and that's just fine! But part of this project is for you to practice the tools we learned in class, which is dplyr and ggplot2.

**Summarizing:**

1.  Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.
2.  Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!
3.  Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks! *An example: age in years into "child, teen, adult, senior".*
4. Compute the proportion and counts in each category of one categorical variable across the groups of another categorical variable from your data. Do not use the function `table()`!

**Graphing:**

6. Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are "pretty" or easier to read.
7. Make a graph where it makes sense to customize the alpha transparency.

Using variables and/or tables you made in one of the "Summarizing" tasks: 

8. Create a graph that has at least two geom layers. 
9. Create 3 histograms, with each histogram having different sized bins. Pick the "best" one and explain why it is the best.

Make sure it's clear what research question you are doing each operation for!

<!------------------------- Start your work below ----------------------------->
For the first research question "Do newer apartments have more elevators?" we will look at completing Task 3 to summarize our numerical variable of the number of elevators into 3 groups: few, moderate, and many. Few will be less than 3, moderate will be 3 to 4, and many will be more than 4 elevators. By doing so, we are able to then use this data and graph it so we can visually see if apartments with more elevators tend to be newer.

```{r}
###This code creates the new categorical variable using the mutate function.
apt_buildings <- apt_buildings %>%
  mutate(
    `AmountOfElev` = case_when(
      no_of_elevators < 3 ~ "Few",
      no_of_elevators >= 3 & no_of_elevators <= 4 ~ "Moderate",
      no_of_elevators > 4 ~ "Many",
      TRUE ~ "unknown"
    )
  )
###This code displays what our newly created variable looks like
apt_buildings %>%
select('AmountOfElev')

```

Using the data above, we will create a side-by-side boxplot to compare the spread of the years that the apartments were built in for each group. We also want to be able to see individual points as well so we will use both geom_boxplot and geom_point (Task 8).


```{r}
###We are going to reorder the levels of our variable "ParkingSpace" so it reads better when we graph it in the next part
apt_buildings <- apt_buildings %>%
  mutate(AmountOfElev = factor(AmountOfElev, levels = c("Few", "Moderate", "Many")))
  

###This creates the boxplot and the points on it
apt_buildings %>%
  ggplot(aes(x = AmountOfElev, y = year_built)) +
  geom_boxplot() +
  labs(title = "Year Built vs. Amount of Elevators",
       x = "Amount Of Elevators",
       y = "Year Built") +
  geom_point(position = position_jitter(width = 0.2), size = 2, aes(color = AmountOfElev), alpha = 0.1) +
  scale_color_manual(values = c("Few" = "red", "Moderate" = "gold", "Many" = "green4")) +
  theme_bw()
```

From the graph above, we can see that the amount of elevators and the year built does not seem to have a significant association. Of course, we do have a lot less data points for the "many" group, but even within that group, we can still see that the majority were built around 1980s'.




Now we will look at the second research question "Does the year of the apartment built affect the presence of fire alarms?" 

We will complete (Task 2) and compute the number of observations for this variable. First, we will group the data by the "fire_alarm" variable.

```{r}
###This code creates a separate data frame that will allow us to pull the counts of each group within the variable
fire_alarm_counts <- apt_buildings %>%
  group_by(fire_alarm) %>%
  summarize(count = n())

print(fire_alarm_counts)
```

```{r}
###These codes pull the counts for each group and computes the number of observations for this variable
yes_count <- fire_alarm_counts %>%
  filter(fire_alarm == "YES") %>%
  pull(count)

no_count <- fire_alarm_counts %>%
  filter(fire_alarm == "NO") %>%
  pull(count)

print(yes_count)
print(no_count)
```
So in general, it seems that most apartments do have a fire alarm, regardless of the year built. However, we know that 12 apartments do not have a fire alarm. But what does the distribution look like regarding the year that these apartments were built in? Let's create a graph to see if we can find any interesting results! In fact, we will create 3 histograms with different bin sizes to see which one fits our purpose best! (Task 9)



Histogram with bin size = 1

```{r}
###This code first filters the "fire_alarm" variable and only looks at the data with "NO". Then it creates a histogram
NoFireAlarm <- apt_buildings %>%
  filter(fire_alarm == "NO")

ggplot(NoFireAlarm, aes(x = year_built)) +
  geom_histogram(binwidth = 1, fill = "white", color = "black") +
  labs(title = "Distribution of Apartments with No Fire Alarm by Year Built",
       x = "Year Built",
       y = "Count") +
  theme_bw()

```
Histogram with bin size = 10

```{r}
###This code is identical to the one above, but with a bin size of 10
NoFireAlarm <- apt_buildings %>%
  filter(fire_alarm == "NO")

ggplot(NoFireAlarm, aes(x = year_built)) +
  geom_histogram(binwidth = 10, fill = "white", color = "black") +
  labs(title = "Distribution of Apartments with No Fire Alarm by Year Built",
       x = "Year Built",
       y = "Count") +
  theme_bw()

```

Histogram with bin size = 30

```{r}
###This code is identical to the one above, but with a bin size of 30
NoFireAlarm <- apt_buildings %>%
  filter(fire_alarm == "NO")

ggplot(NoFireAlarm, aes(x = year_built)) +
  geom_histogram(binwidth = 30, fill = "white", color = "black") +
  labs(title = "Distribution of Apartments with No Fire Alarm by Year Built",
       x = "Year Built",
       y = "Count") +
  theme_bw()

```

From the graphs above, I personally think the bin size of 1 is a bit too small. Also, we're not too heavily focused on the exact year that these buildings were built in, but rather the overall distribution to check if the apartments with no fire alarms tend to be built earlier on. As such, I would say the second graph with a bin size of 10 looks the nicest and also provides us with the information that we need. From previous graphs, we know that a lot of the buildings were built around the 1950-1960's so it's not a surprise that the distribution of apartments with no fire alarms look like this. It also shows that there is a new apartment (built around 2000) without fire alarms as well, so overall, the presence (or the lack of) of fire alarms seem similar regardless of the year built.




Now we are going to look at our third research question "Are newer apartments taller?"


For this part, the numerical variable "no_of_storeys" will be used to create a categorical variable (Task 3). The new categorical variable will have groups "short, medium, tall" to describe approximately how tall our apartments are. This allows us to quickly determine if the building is tall or short by categorize the height of each building into 3 groups. In this analysis, we will say that an apartment that has less than 10 storeys will be considered "short," 10-20 storeys will be considered "medium," and more than 20 storeys will be considered "tall." 


```{r}
###This code creates the new categorical variable using the mutate function.
apt_buildings <- apt_buildings %>%
  mutate(
    `Height of building` = case_when(
      no_of_storeys < 10 ~ "Short",
      no_of_storeys >= 10 & no_of_storeys <= 20 ~ "Medium",
      no_of_storeys > 20 ~ "Tall",
      TRUE ~ "unknown"
    )
  )
###This code displays what our newly created variable looks like
apt_buildings %>%
select('Height of building')
```
Since we have our new variable, let's create a bar graph (Task 6) to display this data. We will make the y-axis logarithmic and edit the axis labels to make the graph look nicer.  

```{r}
###We are going to reorder the levels of our variable "Height of buildling" so it reads better when we facet it in the next part
apt_buildings <- apt_buildings %>%
  mutate(`Height of building` = factor(`Height of building`, levels = c("Short", "Medium", "Tall")))

###This code creates a faceted bar graph that displays how many buildings built in different years are short, medium, and tall
ggplot(apt_buildings, aes(x = `year_built`, fill = `Height of building`)) +
  geom_bar(position = position_dodge(width = 1)) +
  labs(x = "Year Built", y = "# of Apartments") +
  scale_y_log10() +
  ggtitle("Overview of Apartment Height Relative to the Year Built") +
  scale_fill_manual(values = c("Short" = "red", "Medium" = "gold", "Tall" = "green4")) +
  theme_bw() +
  facet_wrap(~`Height of building`)
```
From this graph, we can easily see that generally, taller buildings were built later, especially since we do not see any tall buildings before the 1950's.


Lastly, We will explore our last research question "Do newer apartments come with more parking spaces?" 

To investigate this, similar to what we did for the first and third research question, we will create 3 groups for our parking spaces: Few, Moderate, and Many (Task 3). Less than 10 will be "Few", 10 to 20 will be "Moderate" and more than 20 will be "Many." This will allow us to easily categorize each observation.


```{r}
###This code creates the new categorical variable using the mutate function.
apt_buildings <- apt_buildings %>%
  mutate(
    `ParkingSpace` = case_when(
      no_of_accessible_parking_spaces < 10 ~ "Few",
      no_of_accessible_parking_spaces >= 10 & no_of_accessible_parking_spaces <= 20 ~ "Moderate",
      no_of_accessible_parking_spaces > 20 ~ "Many",
      TRUE ~ "unknown"
    )
  )
###This code displays what our newly created variable looks like
apt_buildings %>%
select('ParkingSpace')
```

Since we have our new variable, let's create a bar graph (Task 6) to display this data. We will make the y-axis logarithmic and edit the axis labels to make the graph look nicer.

```{r}
###We are going to reorder the levels of our variable "ParkingSpace" so it reads better when we facet it in the next part
apt_buildings <- apt_buildings %>%
  mutate(ParkingSpace = factor(ParkingSpace, levels = c("Few", "Moderate", "Many"))) 

###This code creates a faceted bar graph that displays how many buildings built in different years have few, moderate, and many parking spaces
ggplot(apt_buildings, aes(x = `year_built`, fill = `ParkingSpace`)) +
  geom_bar(position = position_dodge(width = 1)) +
  labs(x = "Year Built", y = "# of Apartments") +
  scale_y_log10() +
  ggtitle("Overview of Parking Spaces Relative to the Year Built") +
  scale_fill_manual(values = c("Few" = "red", "Moderate" = "gold", "Many" = "green4")) +
  theme_bw() +
  facet_wrap(~`ParkingSpace`)
```
From the graph above, it doesn't seem like newer apartments have more parking spaces. If anything, it seems like most of the apartments with many parking spaces were built between 1950 to 1975. 
<!----------------------------------------------------------------------------->

### 1.3 (2 points)

Based on the operations that you've completed, how much closer are you to answering your research questions? Think about what aspects of your research questions remain unclear. Can your research questions be refined, now that you've investigated your data a bit more? Which research questions are yielding interesting results?

<!------------------------- Write your answer here ---------------------------->
I think these operations got me a decent understanding of answering my research questions. We can see that except for the third question which was "Are newer apartments taller?", the year of the apartment being built necessarily did not mean that it had an impact on the other 3 variables in the other research questions, which were number of elevators, presence of fire alarms, and number of parking spaces. This suggests that regarding these variables, an apartment being newer did not mean that it was better.

However, we did see that taller apartments generally were built more recently, which helps to answer my overarching question of "Are newer apartments better?" It does seem that the taller buildings are relatively newer, which makes them a lot cooler than short, old apartments.

<!----------------------------------------------------------------------------->

# Task 2: Tidy your data 

In this task, we will do several exercises to reshape our data. The goal here is to understand how to do this reshaping with the `tidyr` package.

A reminder of the definition of *tidy* data:

-   Each row is an **observation**
-   Each column is a **variable**
-   Each cell is a **value**

### 2.1 (2 points)

Based on the definition above, can you identify if your data is tidy or untidy? Go through all your columns, or if you have \>8 variables, just pick 8, and explain whether the data is untidy or tidy.

<!--------------------------- Start your work below --------------------------->
Let's look at our data.

```{r}
head(apt_buildings)
```
Since we have a lot of data, we are going to choose 8 variables: separate_water_meters, separate_hydro_meters, separate_gas_meters, fire_alarm, heating_type, intercom, laundry_room, no_of_elevators. We can see that each row is an observation (a specific apartment), each of these variables listed above is a column, and the cells are the values for the variables/columns. So we have a tidy data! 

<!----------------------------------------------------------------------------->

### 2.2 (4 points)

Now, if your data is tidy, untidy it! Then, tidy it back to it's original state.

If your data is untidy, then tidy it! Then, untidy it back to it's original state.

Be sure to explain your reasoning for this task. Show us the "before" and "after".

<!--------------------------- Start your work below --------------------------->
We will first load tidyr

```{r}
library(tidyr)
```

We will take the three variables, separate_gas_meters, separate_hydro_meters, and separate_water_meters, and use pivot_longer. We will make new variables called "TypeOfMeter" and "PresenceOfMeter". The resulting dataset would be untidy, since the TypeOfMeter variable combines information about different types of meters.

```{r}
###I will pivot longer into a new version of the data so we don't have to worry about accidentally messing up other stuff in the process and have the untidy version remaining for further use later if needed.
apt_buildings_untidy_data <- apt_buildings %>%
  pivot_longer(
    cols = c(`separate_gas_meters`, `separate_hydro_meters`, `separate_water_meters`),
    names_to = "TypeOfMeter",
    values_to = "PresenceOfMeter"
  )
```


```{r}
###This prints our untidy data
print(apt_buildings_untidy_data)

```

Now let's use pivot_wider and get our data back to the original format.

```{r}
###This uses pivot_wider to revert the changes back to normal
back_to_original <- apt_buildings_untidy_data %>%
  pivot_wider(
    names_from = TypeOfMeter,
    values_from = PresenceOfMeter
  )

###This displays our reverted data
print(back_to_original)
```
We can see that we have our original variables/columns back! We have successfully reverted the changes.

<!----------------------------------------------------------------------------->

### 2.3 (4 points)

Now, you should be more familiar with your data, and also have made progress in answering your research questions. Based on your interest, and your analyses, pick 2 of the 4 research questions to continue your analysis in the remaining tasks:

<!-------------------------- Start your work below ---------------------------->

1.  Are newer apartments taller?
2.  Does the year of the apartment built affect the presence of fire alarms?

<!----------------------------------------------------------------------------->

Explain your decision for choosing the above two research questions.

<!--------------------------- Start your work below --------------------------->
I chose these research questions because I believe that they provide a variety of observations/data to answer my overarching question of "Are newer apartments better?" As I mentioned previously, I really do believe the best part about an apartment is the fact that they are tall. If so, I think it is crucial to focus on the research question "Are newer apartments taller?" to answer my overarching question. I also chose the question "Does the year of the apartment built affect the presence of fire alarms?" as this question considers the safety aspects of what makes a "good" apartment. If I were to only focus on the height of the building, but the buildings were very unsafe, that wouldn't make it a very good apartment overall. So I wanted to choose the other research question that could answer the safety aspect as well.
<!----------------------------------------------------------------------------->

Now, try to choose a version of your data that you think will be appropriate to answer these 2 questions. Use between 4 and 8 functions that we've covered so far (i.e. by filtering, cleaning, tidy'ing, dropping irrelevant columns, etc.).

(If it makes more sense, then you can make/pick two versions of your data, one for each research question.) 

<!--------------------------- Start your work below --------------------------->
```{r}
###We will first remove unnecessary variables by choosing only the ones we need
apt_buildings_new <- apt_buildings %>%
  select(year_built, fire_alarm, no_of_storeys, `Height of building`) %>%

###Now we rename the variables using CamelCase     
  rename(YearBuilt = year_built, FireAlarm = fire_alarm, NumberOfFloors = no_of_storeys, HeightOfBuilding = 'Height of building') %>%

###We will also arrange the dataset by the year built to make it look nice and ascending based on year, since that is our main focus in this research
  arrange(YearBuilt) %>%
  
###Then finally, we will drop the rows with missing data
  drop_na()
  
head(apt_buildings_new)
```
<!----------------------------------------------------------------------------->

# Task 3: Modelling

## 3.0 (no points)

Pick a research question from 1.2, and pick a variable of interest (we'll call it "Y") that's relevant to the research question. Indicate these.

<!-------------------------- Start your work below ---------------------------->

**Research Question**: Are newer apartments taller?

**Variable of interest**: NumberOfFloors

<!----------------------------------------------------------------------------->

## 3.1 (3 points)

Fit a model or run a hypothesis test that provides insight on this variable with respect to the research question. Store the model object as a variable, and print its output to screen. We'll omit having to justify your choice, because we don't expect you to know about model specifics in STAT 545.

-   **Note**: It's OK if you don't know how these models/tests work. Here are some examples of things you can do here, but the sky's the limit.

    -   You could fit a model that makes predictions on Y using another variable, by using the `lm()` function.
    -   You could test whether the mean of Y equals 0 using `t.test()`, or maybe the mean across two groups are different using `t.test()`, or maybe the mean across multiple groups are different using `anova()` (you may have to pivot your data for the latter two).
    -   You could use `lm()` to test for significance of regression coefficients.

<!-------------------------- Start your work below ---------------------------->
To test whether newer apartments tend to be taller, we can perform a linear regression analysis. We can use 'lm()' to fit a linear regression model to our variable of interest. Our y will be the number of floors and our x will be the year built.

```{r}
###This fits a linear regression model with respect to my research question
model <- lm(NumberOfFloors ~ YearBuilt, data = apt_buildings_new)

###This prints the result
print(model)
```

<!----------------------------------------------------------------------------->

## 3.2 (3 points)

Produce something relevant from your fitted model: either predictions on Y, or a single value like a regression coefficient or a p-value.

-   Be sure to indicate in writing what you chose to produce.
-   Your code should either output a tibble (in which case you should indicate the column that contains the thing you're looking for), or the thing you're looking for itself.
-   Obtain your results using the `broom` package if possible. If your model is not compatible with the broom function you're needing, then you can obtain your results by some other means, but first indicate which broom function is not compatible.

<!-------------------------- Start your work below ---------------------------->
We will load broom first.
```{r}
library(broom)
```
Then we will use tidy() to get a statistical summary of our model and look at the column 'p-value' to get our p-value of the intercept and the predictor (YearBuilt).

```{r}
tidy(model)
```

We can see that the p-value is 7.89804e-107 and 2.10415e-113 for the intercept and the predictor (YearBuilt) respectively.

<!----------------------------------------------------------------------------->

# Task 4: Reading and writing data

Get set up for this exercise by making a folder called `output` in the top level of your project folder / repository. You'll be saving things there.

## 4.1 (3 points)

Take a summary table that you made from Task 1, and write it as a csv file in your `output` folder. Use the `here::here()` function.

-   **Robustness criteria**: You should be able to move your Mini Project repository / project folder to some other location on your computer, or move this very Rmd file to another location within your project repository / folder, and your code should still work.
-   **Reproducibility criteria**: You should be able to delete the csv file, and remake it simply by knitting this Rmd file.

<!-------------------------- Start your work below ---------------------------->
We will first load the package 'readr' and 'here' to do this. 
```{r}
library(readr)
library(here)
```


```{r}
###This defines the output file path
file_path <- here("output", "fire_alarm_counts.csv")

###This writes the summary table to a CSV file
write_csv(fire_alarm_counts, file_path)


```
<!----------------------------------------------------------------------------->

## 4.2 (3 points)

Write your model object from Task 3 to an R binary file (an RDS), and load it again. Be sure to save the binary file in your `output` folder. Use the functions `saveRDS()` and `readRDS()`.

-   The same robustness and reproducibility criteria as in 4.1 apply here.

<!-------------------------- Start your work below ---------------------------->
```{r}

# Define the output file path for the RDS file using here::here()
model_path <- here("output", "model.rds")

# Save the model object to an RDS file
saveRDS(model, model_path)

# Load the model object from the RDS file
loaded_model <- readRDS(model_path)
```
<!----------------------------------------------------------------------------->

# Overall Reproducibility/Cleanliness/Coherence Checklist 

Here are the criteria we're looking for.

## Coherence (0.5 points)

The document should read sensibly from top to bottom, with no major continuity errors. 

The README file should still satisfy the criteria from the last milestone, i.e. it has been updated to match the changes to the repository made in this milestone. 

## File and folder structure (1 points)

You should have at least three folders in the top level of your repository: one for each milestone, and one output folder. If there are any other folders, these are explained in the main README.

Each milestone document is contained in its respective folder, and nowhere else.

Every level-1 folder (that is, the ones stored in the top level, like "Milestone1" and "output") has a `README` file, explaining in a sentence or two what is in the folder, in plain language (it's enough to say something like "This folder contains the source for Milestone 1").

## Output (1 point)

All output is recent and relevant:

-   All Rmd files have been `knit`ted to their output md files. 
-   All knitted md files are viewable without errors on Github. Examples of errors: Missing plots, "Sorry about that, but we can't show files that are this big right now" messages, error messages from broken R code
-   All of these output files are up-to-date -- that is, they haven't fallen behind after the source (Rmd) files have been updated.
-   There should be no relic output files. For example, if you were knitting an Rmd to html, but then changed the output to be only a markdown file, then the html file is a relic and should be deleted.

Our recommendation: delete all output files, and re-knit each milestone's Rmd file, so that everything is up to date and relevant.

## Tagged release (0.5 point)

You've tagged a release for Milestone 2. 

### Attribution

Thanks to Victor Yuan for mostly putting this together.